---
title: "The MultiLA software platform"
author:
  - name: "Markus Konrad"
    affil: 1
    main: true
    email: "markus.konrad@htw-berlin.de"
  - name: Maria Osipenko
    affil: 2
    main: true
    email: "osipenko@hwr-berlin.de"
  - name: Martin Spott
    affil: 1
    main: true
    email: "martin.spott@htw-berlin.de"
  - name: Andre Beinrucker
    affil: 1
    main: true
    email: "beinrucker@htw-berlin.de"
affiliation:
  - num: 1
    address: Hochschule für Technik und Wirtschaft Berlin
  - num: 2
    address: Hochschule für Wirtschaft und Recht Berlin
main_findings:
  - "Authoring and learning analytics for e-learning applications in data science education"
logoleft_name: "img/htw_logo.jpg"
logoright_name: "img/hwr_logo.png"
logocenter_name: "img/ifaf_logo.jpg"
poster_width: "841mm"
poster_height: "1189mm"
main_topsize: 0.2
main_bottomsize: 0.1
main_fontfamily: 'BlinkMacSystemFont, "Segoe UI", Roboto, Oxygen, Ubuntu, Cantarell, "Fira Sans", "Droid Sans", "Helvetica Neue", sans-serif'
main_textcol: "#ffffff"
font_family: 'BlinkMacSystemFont, "Segoe UI", Roboto, Oxygen, Ubuntu, Cantarell, "Fira Sans", "Droid Sans", "Helvetica Neue", sans-serif'
primary_colour: "#5faaea"
secondary_colour: "#5faaea"   # "#e5f1fb"
accent_colour: "#3eaf7c"
output: 
  posterdown::posterdown_betterport:
    self_contained: true
    pandoc_args: --mathjax
    number_sections: false
bibliography: packages.bib
link-citations: true
knit: pagedown::chrome_print
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      tidy = FALSE,
                      message = FALSE,
                      fig.align = 'center',
                      out.width = "100%")
options(knitr.table.format = "html") 
```

# Introduction

This is the `posterdown_betterport` template for the {posterdown} package! I was inspired by the twitter thread of [Mike Morrison](https://mobile.twitter.com/mikemorrison/status/1110191245035479041) and wanted to apply the `#betterposter` concept to the reproducible (yet simple to use) functionality of the {posterdown} package [@R-posterdown]. If you're not an R user don't sweat as you do **NOT** need to use it at all! Feel free to use only the Markdown functionality of this package :)

```{r, include=FALSE}
knitr::write_bib(c('posterdown', 'rmarkdown','pagedown'), 'packages.bib')
```

## Objectives

1. Pick a template layout.
2. Write/ create your poster content distraction free.
3. Let posterdown do its thing!

# Methods

I will show here how to include poster elements that may be useful, such as an equation using mathjax:

$$
E = mc^2
$$

To reference a citation you can add your `.bib` file to the working directory and name it in the YAML metadata or generate an automated one as done here, then you only need to reference the label value in the `.bib` file. For example this package is built on top of the wonderful {pagedown} package and I will cite it at the end of this sentance using this in the rmd `[@R-pagedown]` [@R-pagedown].

To get a better understanding of how to include features like these please refer to the {posterdown} [wiki](https://github.com/posterdown/wiki).

**_Now on to the results!_**

# Results

Here you may have some figures to show off, bellow I have made a scatterplot with the infamous Iris dataset and I can even reference to the figure automatically like this, `Figure \@ref(fig:irisfigure)`, Figure \@ref(fig:irisfigure).

```{r, irisfigure, fig.cap='Here is a caption for the figure. This can be added by using the "fig.cap" option in the r code chunk options, see this [link](https://yihui.name/knitr/options/#plots) from the legend himself, [Yihui Xie](https://twitter.com/xieyihui).', out.width="80%"}
par(mar=c(2,2,0,1))
plot(x = iris$Sepal.Length, y = iris$Sepal.Width,
     col = iris$Species, pch = 19, xlab = "Sepal Length",
     ylab = "Sepal Width")
```

Maybe you want to show off some of that fancy code you spent so much time on to make that figure, well you can do that too! Just use the `echo=TRUE` option in the r code chunk options, Figure \@ref(fig:myprettycode)!

```{r myprettycode, echo=TRUE, fig.cap='Boxplots, so hot right now!', fig.height=6, out.width="80%"}
#trim whitespace
par(mar=c(2,2,0,0))
#plot boxplots
boxplot(iris$Sepal.Width~iris$Species,
        col = "#008080", 
        border = "#0b4545",
        ylab = "Sepal Width (cm)",
        xlab = "Species")
```

How about a neat table of data? See, Table \@ref(tab:iristable):

```{r, iristable}
knitr::kable(
  iris[1:15,1:5], format = "html",
  caption = "A table made with the **knitr::kable** function.",
  align = "c", col.names = c("Sepal <br> Length",
                             "Sepal <br> Width",
                             "Petal <br> Length",
                             "Petal <br> Width",
                             "Species"),
  escape = FALSE)
```

# References
